Bibliographic Survey\\\medskip Research Project 2022

### 2022-10-03 biblio-rp.tex
typos

\subsection{Proof-of-Stake}
The first occurrence of Proof-of-Stake can be found behind the cryptocurrency PPCoin (or PeerCoin) \cite{ppcoin}, a project receiving very little interest nowadays. However, the technology gained popularity over time and nowadays much more cryptocurrencies are based on Proof-of-Stake than on Proof-of-Work \cite{coinmarketcap}. 
The second biggest cryptocurrency by market cap\footnote{Market capitalization (or market cap) is the total value of all the coins that have been mined. It is calculated by multiplying the number of coins in circulation by the current market price of a single coin.}, Ethereum, even moved from Proof-of-Work to Proof-of-Stake not long before these lignes are written, in on of the biggest event the world of crypto has ever seen (known as The Merge).

Proof-of-Stake consists in replacing the trust from computing power with the trust from holding the coins of the ecosystem, therefore prooving that someone has something to loose beeing dishonest.

>>>>

\subsection{Proof-of-Stake}
The first occurrence of Proof-of-Stake can be found behind the cryptocurrency PPCoin (or PeerCoin) \cite{ppcoin}, a project receiving very little interest nowadays. However, the technology gained popularity over time and nowadays much more cryptocurrencies are based on Proof-of-Stake than on Proof-of-Work \cite{coinmarketcap}. 
The second biggest cryptocurrency by market cap\footnote{Market capitalization (or market cap) is the total value of all the coins that have been mined. It is calculated by multiplying the number of coins in circulation by the current market price of a single coin.}, Ethereum, even moved from Proof-of-Work to Proof-of-Stake not long before these lignes were written, in one of the biggest event the world of crypto has ever seen (known as The Merge).

Proof-of-Stake consists in replacing the trust from computing power with the trust from holding the coins of the ecosystem, therefore prooving that someone has something to loose by beeing dishonest.
